Regional and Urban Economics

### 2023-02-19 Retail Agglomeration_Theory.qmd
stuff added

A simple explanation of why two dentists providing the same service, at the same price might locate next to each other.
Nevertheless, despite increasing the transportation cost for patients.
Perhaps the simplest way to explain why there is a natural tendency for retailers to cluster in space; a tendency which may help explain the existence of larger agglomerations.

>>>>

A simple explanation of why two dentists providing the same service, at the same price might locate next to each other.
Nevertheless, despite increasing the transportation cost for patients.
Perhaps the simplest way to explain why there is a natural tendency for retailers to cluster in space; a tendency which may help explain the existence of larger agglomeration economies.
